---
title: "Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE
)
```

All dependencies for this project should be listed in the DESCRIPTION FILE. This ensures that anyone that wishes to run the app can simply install this package.

The project is a shiny app as a package which ensures that the management of any functions, modules and additional assets is self-contained providing a final runnable application with a simple function call.

An update for the application can be made by editing the source code and rebuilding the package. An example app runner can be viewed in an RStudio session with

```{r}
file.edit(system.file("example", "app.R", package = "diagramNAT"))
```

Note there are some other build requirements if some of the custom JavaScript is to be edited. In particular the assets that are created using the React framework. See the section on React dependencies

## TRAVIS

The repository that this package is developed in uses [TRAVIS](https://travis-ci.org/) to automate certain elements of the build and deploy step. The build is described in the `.travis.yml` file. In short though the current build routine is as follows

* Expose the CI runner to all the R package repositories it might need (i.e CRAN and BioConductor)
* Attempt to install all package dependencies listed in the DESRIPTION FILE
* Attempt to build this package
* If successful, use the branch name to deploy an updated version of the application by running the `deploy_to_shinyapps.R` script

### Deploying to shinyapps.io

The current deployment script will 

* Install the package in-line with the source and dependencies specified on the specific branch
* Attempt to deploy a branch-named version of the application to the specified account name on the specified server
    * To do this it uses a couple of environment variables to authenticate with the shinyapps.io account
    * `shinyapps_io_token` - a token generated from the shinyapps.io account
    * `shinyapps_io_secret` - the associated secret for the token
* Since the auto deployment will run for updates on any branch the script will also attempt to clean up after itself in the event that
    * A branch is merged back into master
    * A branch is deleted

## R source code

The bulk of the application is organised into [modules](https://shiny.rstudio.com/articles/modules.html) and functions. As I tidy up these are being further organised by naming conventions to help highlight the utility of a given function and or module.

* `X_tab.R` files typically describe a function for a tab in the dashboard that does not require complex user interaction and communication from server to client and back. For example the home tab landing page for the application.
* `X_module.R` contain source for the user interface and server side logic for a given module. Utility functions specific to the module should also be found here.
* `ui.R` and `server.R` contain the top-level client and server side functions (similar to the set up of a normal shiny app) with the difference that these are functions, that can take additional arguments, for setting up the objects necessary for a specific instance of the application.
* `run_app.R` contains the topmost level wrapper which returns a `shinyApp` object, which is used to actually run an application. See for example the `app.R` in the `inst/example` directory.


### Modularisation

The advantage of modularisation of a shiny app is that individual separate pieces of user interface and server side logic can be separated from the rest of the application. This also allows us to run and test these individual pieces without requiring the full application. Some of the module script files have such examples commented out at the bottom of the source file as I used them while wanting to quickly iterate on a particular modules functionality. I have left these in where appropriate as a guideline if you want to examine this.

## React dependencies

This project uses React to create some of the user interface elements that use custom javascript. These require an additional build step should someone wish to update the functionality.

### Pre-requisites

In order to develop the React components for this package, you will need to install (in addition to R)

* [Node.js](https://nodejs.org/) JavaScript engine and runtime for development outide of browsers. Provides the `node` and `npm` commands.
* [Yarn](https://yarnpkg.com/en/) Command-line dependency management tool, provides the `yarn` command.

### Managing the JavaScript dependecies

JavaScript dependecies are installed and updated via the node package manager (npm) using the yarn command line utility. The collection of JavaScript dependencies is described in the `package.json` file at the root of the R package. To install/update depencies

```
yarn install
```

### React source

The source code for react elements is [modern JavaScript](https://babeljs.io/docs/en/babel-preset-env) with [JSX](https://babeljs.io/docs/en/babel-preset-react) which will be transpiled to a dialect of JavaScript that most browsers understand as part of the build step.

### Transpiling the React source

To create the final JavaScript assets for inclusion in the R package we can

```
yarn run webpack
```

which delegates to the [webpack](https://webpack.js.org/) program to build the final assets as described in `webpack.config.js`

### R wrapper for React components

Each React component also has a dedicated R function wrapper which handles passing of data to and from the created JavaScript widgets. See for example the source code of `customSliderTripleInput` or refer to the very useful ReactR tutorial at https://react-r.github.io/reactR/articles/intro_inputs.html.

## Other assets

### PDF

The package contains a pdf template style based on the branding guide that we received. This is used for the purpose of rendering the reports that users can download and was also used in creating the downloadable questions. The assets for this template are found under `inst/rmarkdown` in line with the standard approach to creating new rmarkdown templates. A useful guide to creating such templates is found at https://bookdown.org/yihui/rmarkdown/document-templates.html. 

The directory contains all of the necessary assets for style and layout. In particular `inst/rmarkdown/templates/nata-report/resources/template.tex` is where the fonts and colours are set for the documents.
