---
output: diagramAPI::pdf_report
params:
  req: NA # all objects to be viewed
header-includes:
  - \usepackage{tabu}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = TRUE, message = FALSE)
library(magrittr)
# req = params$req
# req = diagramAPI:::test_req_csv("mixed_simple")$postBody %>%
#     jsonlite::parse_json() %>%
#     diagramAPI:::extract_responses()
models = diagramAPI::group_objects_by_model(req)
```

DiAGRAM produces a risk prevention score for the digital preservation outcomes of renderability and intellectual control.

* Renderability - The object is a sufficiently useful representation of the original file.
* Intellectual Control - Having full knowledge of the material content, provenance and conditions of use.

The higher the score, the lower the risk to the digital archive.

```{r, results='asis'}
purrr::walk(models, function(model_name) {
  e = new.env(parent = knitr::knit_global())
  message(model_name)
  e$params = list(
    req = model_name
  )
  cat(paste(
    suppressMessages(knitr::knit_child("pdf_section.Rmd", envir = e, quiet = TRUE)),
    collapse = "\n"
  ))
})
```

