---
output: diagramNAT::pdf_report
params:
  question_data: NA
  download_data: NA
  vis_data: NA
---

```{r setup, include = FALSE}
question_data = params$question_data
download_data = params$download_data
vis_data = params$vis_data

# for now we want to trim out custom models
# is_custom = download_data %>% 
#   dplyr::filter(.data$`Custom Model`)%>%
#   dplyr::distinct(.data$Model, .data$Policy)
# 
# dplyr::anti_join(download_data, is_custom)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

models = unique(vis_data$Model)
```

DiAGRAM produces a risk prevention score for the digital preservation outcomes of renderability and intellectual control.

* Renderability - The object is a sufficiently useful representation of the original file.
* Intellectual Control - Having full knowledge of the material content, provenance and conditions of use.

The higher the score, the lower the risk to the digital archive.

```{r, results='asis'}
purrr::walk(models, function(model_name) {
  e = new.env(parent = knitr::knit_global())
  e$params = list(question_data = question_data, download_data = download_data, vis_data = vis_data, model_name = model_name)
  cat(paste(suppressMessages( knitr::knit_child('pdf_section.Rmd', envir = e, quiet = TRUE)), collapse = "\n"))
})
# cat(paste(out, collapse = "\n"))
```

